### 2017-11-06 monograph/thesis/chapters/motivation.tex
Fixed Sublime Text LatexTools (Log parsing issues. Disregard unless
something else is wrong.), issue:
(Log parsing issues. Disregard unless something else is wrong.)
https://github.com/SublimeText/LaTeXTools/issues/1216
Split the object_beautifier.tex The Problem section to other
related chapters.
Created the Code Beautifying section on motivation.tex

    Coding is like writing and reading a book for the large people, you like it
    to look beautifully. Or at least do you expect such when you buy a book, for
    example, to learn programming for you first time. You expect: % Reference to
    % book writing style/formatting articles

    \begin{enumerate}
        \item Things to be well organized, so you do not get lost.

        \item The colors to be properly placed, so you do not get distracted
           from the main content.

        \item The spacing between paragraphs, words, chapters, sections
           subsections, etc, to be well adjusted. Not everything cluttered in
           only one file, line, function, class, or whatsoever so.
    \end{enumerate}

@@

\end{englishtext}

>>>>

    Coding is like writing and reading a book for the large people, you like it
    to look beautifully. Or at least do you expect such when you buy a book, for
    example, to learn programming for you first time \cite{howNovicesRead}.
    You expect:

    \begin{enumerate}
        \item Things to be well organized, so you do not get lost.
        \item The colors to be properly placed, so you do not get distracted
              from the main content.
        \item The spacing between paragraphs, words, chapters, sections
              subsections, etc, to be well adjusted. Not everything cluttered in
              only one file, line, function, class, or whatsoever so.
    \end{enumerate}

@@

    \section{Code Beautifying}

    A robust Code Beautifier can get a lot more complicated just with the basic
    definitions of formatting (\nameref{source_code_beautifiers})
    applied over each language own characteristics
    as for example:

    \begin{enumerate}[nosep,nolistsep]
        \item Add spaces before if\s name as in `if(var)' versus `if (var)'
        \item Add spaces inside if\s as in `if(var)' versus `if( var )'
        \item Add spaces before for\s name as in `for(var)' versus `for (var)'
        \item Add spaces inside for\s as in `for(var)' versus `for( var )'
        \item ...
    \end{enumerate}

    As may be noticed, the list may became quite big, and if fact such big list
    of rules has been implemented.
    Looking over the Beautifier called `Uncrustify'\footnote{\url{https://github.com/uncrustify/uncrustify}},
    we can find about 500 settings with specifications like these above.
